Covid-19 A Spatio-Temporal Investigation.

### 2021-01-09 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The cumulative number of deaths, infections and recovered cases is given by the database, but since these numbers are only available in its daily cumulative form, it was necessary to calculate monthly quantities for each one of the variables between January and December 2020. The population of each country is also available in the database, so in order to better understand the effects of Covid-19

 No banco também é disponibilizada a quantidade de habitantes de cada país, portanto para melhor capturar o impacto do Covid-19 em cada localidade a quantidade de casos, recuperados e mortes foram calculadas de acordo com a razão pelo número de habitantes.

>>>>

 The cumulative number of deaths, infections and recovered cases is given by the database, but since these numbers are only available in its daily cumulative form, it was necessary to calculate monthly quantities for each one of the variables between January and December 2020. The population of each country is also available in the database, so in order to better understand the spatial and the spatio-temporal effects of Covid-19 in each location, it was necessary to calculate the ratio between the number of infections, the number of recovered cases and the quantity of deaths against the population.
